---
title: "Analysis of Global Sewage for Bacterial and Antimicrobial Resistance Genes"
output: html_notebook
---

This notebook explores a dataset containing information on bacterial profiles and antimicrobial resistance genes (ARGs) from global sewage samples. The aim is to identify prevalent bacterial families and assess the distribution and resistance patterns among them.

### Load Libraries and Read Data

```{r}
# Uncomment the following line to install the 'mgnet' package directly from GitHub if not previously installed
#devtools::install_github("Fuschi/mgnet")
```

```{r}
library(tidyverse)
library(mgnet)
```

```{r}
gs <- readRDS("../data/R/global-sewage.rds")
gs # Display the structure and a brief overview of the dataset
```

### Analysis of Taxa Distribution

I conduct an exploration of the distribution of microbial taxa of mOTU AMR genes. 
The study aims to identify and remove rare taxa that could potentially introduce noise into the dataset. I employ measures of taxa prevalence, sum of abundances, and maximum relative abundance. 

```{r, fig.height=9}
gs %>%
  mutate_taxa(
    prevalence = sum(abun>0)/length(abun),
    log10_sum_taxa = log10(sum(abun)),
    log10_max_rel = log10(max(rela))) %>%
  taxa %>%
  pivot_longer(cols = c(prevalence, log10_sum_taxa, log10_max_rel),
               names_to = "measures", values_to = "values") %>%
  ggplot(aes(x = values)) +
  geom_histogram(fill = "lightblue", color = "darkblue", bins = 20) +
  facet_wrap(~ measures + source, scales = "free", nrow = 3) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        strip.text = element_text(size = 12))
```

```{r, fig.height=5}
gs %>%
  split_taxa(source) %>%
  mutate_sample(
    sum_sample_origin = sum(abun)) %>%
  mutate_taxa(
    prevalence = sum(abun>0)/length(abun),
    log10_sum_taxa = log10(sum(abun)),
    log10_max_rel = log10(max(rela)),
    prevalence_pass = prevalence >= .25,
    sum_taxa_pass = case_when(source == "mOTU" ~ log10_sum_taxa >= 2,
                              source == "amr" ~ log10_sum_taxa >= -1),
    max_rel_pass = case_when(source == "mOTU" ~ log10_max_rel >= -1,
                             source == "amr" ~ log10_max_rel >= -4)) %>%
  filter_taxa(prevalence_pass & sum_taxa_pass | max_rel_pass) %>%
  mutate_sample(
    lost_count = sum(abun) / sum_sample_origin) %>%
  meta(.fmt = "tbl") %>%
  select(lost_count, mgnet) %>%
  ggplot(aes(x = lost_count, fill = mgnet)) +
  geom_histogram(position = "dodge", color = "gray", binwidth = .025) +
  labs(fill = "source") +
  theme_bw()
```

```{r}
gs_source_filt <- gs %>%
  split_taxa(source) %>%
  mutate_sample(
    sum_sample_origin = sum(abun)) %>%
  mutate_taxa(
    prevalence = sum(abun>0)/length(abun),
    log10_sum_taxa = log10(sum(abun)),
    log10_max_rel = log10(max(rela)),
    prevalence_pass = prevalence >= .25,
    sum_taxa_pass = case_when(source == "mOTU" ~ log10_sum_taxa >= 2,
                              source == "amr" ~ log10_sum_taxa >= -1),
    max_rel_pass = case_when(source == "mOTU" ~ log10_max_rel >= -1,
                             source == "amr" ~ log10_max_rel >= -4)) %>%
  filter_taxa(prevalence_pass & sum_taxa_pass | max_rel_pass) %>%
  set_norm_CLR()
```

```{r}
merge_mgnet <- function(x, y){
  mgnet(norm = cbind(norm(x), norm(y)),
        meta = meta(x),
        taxa = bind_rows(taxa(x), taxa(y)))
}

gs_netw <- mgnetList(
  "mOTU-ResFinder" = merge_mgnet(gs_source_filt$mOTU,
                                 filter_taxa(gs_source_filt$amr, group_amr == "ResFinder")),
  "mOTU-Functional" = merge_mgnet(gs_source_filt$mOTU,
                                  filter_taxa(gs_source_filt$amr, group_amr == "Functional"))
) %>%
  constructCorrCLRNet(cor_method = "spearman",
                      thresh_method = "absolute", thresh_value = .6) %>%
  cluster_signed()
```

```{r}
gs_netw_filt <- gs_netw %>%
  filter_taxa(n() > 1, .by = c("mgnet","comm_id")) 

map(gs_netw_filt, \(x) sizes(comm(x)))

gs_netw_filt <- gs_netw %>%
  filter_taxa(n() >= 5, .by = c("mgnet", "comm_id")) 
```


```{r}
summary_edges <- map(gs_netw_filt, \(x) {
  df <- igraph::as_data_frame(netw(x))
  df <- cbind(df, "crossing_communities" = igraph::crossing(comm(x), netw(x)))
  }) %>%
  imap(\(x,y) mutate(x, "mgnet" = y, .before = 1)) %>%
  bind_rows() %>%
  mutate(
    new_from = if_else(str_starts(from, "pan_"), to, from),
    new_to = if_else(str_starts(from, "pan_"), from, to)
  ) %>%
  select(mgnet, weight, -from, -to, from = new_from, to = new_to, crossing_communities) %>%
  rename(node_i = from, node_j = to) %>%
  left_join(taxa(gs, "tbl") %>% rename_with(~paste0(., "_i"), -taxa_id), 
            by = join_by(node_i == taxa_id)) %>%
  left_join(taxa(gs, "tbl") %>% rename_with(~paste0(., "_j"), -taxa_id), 
            by = join_by(node_j == taxa_id)) %>%
  unite("link_type", type_i, type_j, sep = "-", remove = FALSE) %>%
  relocate(link_type, .before = crossing_communities)

summary_edges_filt <- summary_edges %>%
  filter(weight>0) %>%
  filter(link_type %in% c("mOTU-Functional","mOTU-ResFinder")) 
```

```{r}
degree_mOTUs <- summary_edges_filt %>%
  group_by(type, mOTU) %>%
  summarise(degree = n(), .groups = "drop")

degree_amr <- summary_edges_filt %>%
  group_by(type, amr) %>%
  summarise(degree = n(), .groups = "drop")

top_amr_fun <- degree_amr %>%
  filter(type == "mOTU-Functional", degree >= 30) 

top_amr_res <- degree_amr %>%
  filter(type == "mOTU-ResFinder", degree >= 5) 
```

### Write Summary Tables

```{r}
taxa(gs_netw_filt, "tbl") %>%
  select(-prevalence,-log10_sum_taxa,-log10_max_rel,
         -prevalence_pass,-sum_taxa_pass,-max_rel_pass) %>%
  write_tsv("../tables/info_nodes.tsv")
  
summary_edges %>%
  write_tsv("../tables/info_edges_all.tsv")

summary_edges_filt %>%
  write_tsv("../tables/info_edges_only_mOTU_AMR.tsv")
```


## Plots

```{r}
#################################################################
# triangle vertex shape
mytriangle <- function(coords, v=NULL, params) {
  vertex.color <- params("vertex", "color")
  if (length(vertex.color) != 1 && !is.null(v)) {
    vertex.color <- vertex.color[v]
  }
  vertex.size <- 1/200 * params("vertex", "size")
  if (length(vertex.size) != 1 && !is.null(v)) {
    vertex.size <- vertex.size[v]
  }

  symbols(x=coords[,1], y=coords[,2], bg=vertex.color,
          stars=cbind(vertex.size, vertex.size, vertex.size),
          add=TRUE, inches=FALSE)
}
# clips as a circle
add_shape("triangle", clip=shapes("circle")$clip,
                 plot=mytriangle)

#################################################################
# generic star vertex shape, with a parameter for number of rays
mystar <- function(coords, v=NULL, params) {
  vertex.color <- params("vertex", "color")
  if (length(vertex.color) != 1 && !is.null(v)) {
    vertex.color <- vertex.color[v]
  }
  vertex.size  <- 1/200 * params("vertex", "size")
  if (length(vertex.size) != 1 && !is.null(v)) {
    vertex.size <- vertex.size[v]
  }
  norays <- params("vertex", "norays")
  if (length(norays) != 1 && !is.null(v)) {
    norays <- norays[v]
  }

  mapply(coords[,1], coords[,2], vertex.color, vertex.size, norays,
         FUN=function(x, y, bg, size, nor) {
           symbols(x=x, y=y, bg=bg,
                   stars=matrix(c(size,size/2), nrow=1, ncol=nor*2),
                   add=TRUE, inches=FALSE)
         })
}
# no clipping, edges will be below the vertices anyway
add_shape("star", clip=shape_noclip,
                 plot=mystar, parameters=list(vertex.norays=5))
```

```{r}
colormap_family <- pull_taxa(gs_netw_filt, "family") %>%
  unlist() %>% table %>% sort(decreasing = T) %>% names %>%
  colormap_categories(distinct_colors = 40)
colormap_family <- colormap_family[colormap_family != "#FFFFFFFF"]

colormap_class_amr <- pull_taxa(gs_netw_filt, "class_amr") %>%
  unlist() %>% table %>% sort(decreasing = T) %>% names %>%
  colormap_categories(distinct_colors = 7)
colormap_class_amr <- colormap_class_amr[colormap_class_amr != "#FFFFFFFF"]

gs_netw_filt <- gs_netw_filt %>%
  mutate_taxa(vertex_color_family_classAMR = case_when(
    source == "mOTU" ~ colormap_family[family],
    source == "amr" ~ colormap_class_amr[class_amr],
  )) 
```

### Networks Family

```{r}
png("../plots/mOTU_amr_family.png", width = 6000, height = 3500, res = 300)

layout(mat = matrix(c(1, 2, 3, 3), ncol = 2, byrow = T), heights = c(6,1))

x <- gs_netw_filt$`mOTU-ResFinder`
set.seed(42)
layout_x <- layout_with_fr(subgraph.edges(netw(x), which(E(netw(x))$weight>0)), 
                           niter = 1000, start.temp = .2)
par(mar=c(0,0,0,0))
plot(x,
     layout = layout_x,
     vertex.label = NA,
     vertex.shape = ifelse(taxa(x)$source == "mOTU", "circle", "star"),
     vertex.size = colMeans(norm(x)) + 3,
     vertex.color = pull_taxa(x, "vertex_color_family_classAMR"),
     vertex.frame.color = ifelse(pull_taxa(x, "source") == "mOTU", "gray90", "black"),
     vertex.frame.width = ifelse(pull_taxa(x, "source") == "mOTU", .2, 1))
mtext("Resifinder", side = 3, line = -4, adj = 0.1, cex = 2) 

x <- gs_netw_filt$`mOTU-Functional`
set.seed(42)
layout_x <- layout_with_fr(subgraph.edges(netw(x), which(E(netw(x))$weight>0)), 
                           niter = 1000, start.temp = .2)
par(mar=c(0,0,0,0))
plot(x,
     layout = layout_x,
     vertex.label = NA,
     vertex.shape = ifelse(taxa(x)$source == "mOTU", "circle", "star"),
     vertex.size = colMeans(norm(x)) + 3,
     vertex.color = pull_taxa(x, "vertex_color_family_classAMR"),
     vertex.frame.width = ifelse(pull_taxa(x, "source") == "mOTU", .2, 1))
mtext("Functional", side = 3, line = -4, adj = .9, cex = 2) 

plot.new()
legend("left", legend = names(colormap_family), fill = colormap_family, title = "mOTU family", ncol = 9, bty = "n")
legend("right", legend = names(colormap_class_amr), fill = colormap_class_amr, title = "amr class", ncol = 2, bty = "n")
#legend(x = .07, y = .2, legend = c("mOTU", "AMR"), pch = c(21, 8),
#       pt.cex = 2, col = c("gray90", "black"),
#       pt.bg = c("gray90", "black"), title = "source", ncol = 2)

dev.off()
```

### Networks Gut

```{r, fig.height=10, fig.width=14}
png("../plots/mOTU_amr_gut.png", width = 6000, height = 3000, res = 300)

layout(mat = matrix(c(1, 2), ncol = 2))

x <- gs_netw_filt$`mOTU-ResFinder`
set.seed(42)
layout_x <- layout_with_fr(subgraph.edges(netw(x), which(E(netw(x))$weight>0)), 
                           niter = 1000, start.temp = .2)
par(mar=c(0,0,0,0))
plot(x,
     layout = layout_x,
     vertex.label = NA,
     vertex.shape = ifelse(taxa(x)$source == "mOTU", "circle", "star"),
     vertex.size = colMeans(norm(x)) + 3,
     vertex.color = if_else(pull_taxa(x,is_from_gut), "brown", "lemonchiffon"),
     #vertex.frame.color = ifelse(pull_taxa(x, "source") == "mOTU", "gray90", "black"),
     vertex.frame.color = taxa(x)$"comm_id",
     vertex.frame.width = 3)
mtext("Resifinder", side = 3, line = -4, adj = 0.1, cex = 2)

x <- gs_netw_filt$`mOTU-Functional`
set.seed(42)
layout_x <- layout_with_fr(subgraph.edges(netw(x), which(E(netw(x))$weight>0)), 
                           niter = 1000, start.temp = .2)
par(mar=c(0,0,0,0))
plot(x,
     layout = layout_x,
     vertex.label = NA,
     vertex.shape = ifelse(taxa(x)$source == "mOTU", "circle", "star"),
     vertex.size = colMeans(norm(x)) + 3,
     vertex.color = if_else(pull_taxa(x,is_from_gut), "brown", "lemonchiffon"),
     #vertex.frame.color = ifelse(pull_taxa(x, "source") == "mOTU", "gray90", "black"),
     vertex.frame.color = taxa(x)$"comm_id",
     vertex.frame.width = 3)
mtext("Functional", side = 3, line = -4, adj = .9, cex = 2) 


dev.off()
```

### Top-Genes Conneted

```{r, fig.height=10, fig.width=4}
png("../plots/Gene-Connected-Functional.png", width = 1200, height = 3000, res = 300)
summary_edges_filt %>%
  filter(type == "mOTU-Functional" & amr %in% top_amr_fun$amr) %>%
  select(amr, family_mOTU) %>%
  group_by(amr, family_mOTU) %>%
  summarise(`edge number` = n(), .groups = "drop") %>%
  arrange(desc(`edge number`)) %>%
  mutate(amr = fct_reorder(amr, `edge number`, .fun = sum, .desc = TRUE)) %>%
  ggplot(aes(x = amr, y = `edge number`, fill = family_mOTU)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = colormap_family) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = .5)) +
  theme(legend.position = "none") +
  ggtitle("Top Gene-Connected Families by AMR") +
  coord_flip() +
  ylim(0,95) +
  theme(title = element_text(size = 10),
        axis.title.y = element_blank()) 
dev.off()
```

```{r, fig.height=10, fig.width=4}
png("../plots/Gene-Connected-ResFinder.png", width = 1200, height = 3000, res = 300)
summary_edges_filt %>%
  filter(type == "mOTU-ResFinder" & amr %in% top_amr_res$amr) %>%
  select(amr, family_mOTU) %>%
  group_by(amr, family_mOTU) %>%
  summarise(`edge number` = n(), .groups = "drop") %>%
  arrange(desc(`edge number`)) %>%
  mutate(amr = fct_reorder(amr, `edge number`, .fun = sum, .desc = TRUE)) %>%
  ggplot(aes(x = amr, y = `edge number`, fill = family_mOTU)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_fill_manual(values = colormap_family) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = .5)) +
  theme(legend.position = "none") +
  ggtitle("Top Gene-Connected Families by AMR") +
  coord_flip() +
  ylim(0,95) +
  theme(title = element_text(size = 10),
        axis.title.y = element_blank()) 
dev.off()
```
